\textbf{\sc Deliberative Autonomy for Marine Robotics}

### 2012-02-02 trunk/europa.tex
Put back algorithm in LaTeX for as I refer to it

The Plan Space Planning algorithm described above can be implemented in many different ways depending on the approach chosen for flaw and resolver selection and for backtracking. EUROPA's built-in solver implements a chronological backtracking algorithm that is summarized in the figure below.

01.  bool solve(PartialPlan plan)
02.   {
03.      if (isInconsistent(plan))  return false;
04.
05.      Flaw flaw = chooseFlaw(plan);
06.      if (flaw == NULL) return true;
07.
08.      DecisionPoint decision = makeDecisionPoint(flaw, plan);
09.
10.      while(decision.hasNext()) {
11.          PartialPlan pp = decision.executeNext();
12.
13.          if (solve(pp)) return true;
14.          else d.undo();
25.      }
16.
17.      return false;
18.  }

@@

\begin{enumerate}
	\item Line 3: Propagate the constraints to test for inconsistency. If found to be inconsistent, then we can return false since this is a dead-end i.e. no refinements to p can yield a consistent plan.
	\item Line 5: Choose a flaw from the set of available flaws.
	\item Line 6: If there are no flaws, then p is complete and we can terminate with success.
	\item Line 8: Otherwise we formulate a decision point which is a branch in the search space. Each choice is a particular refinement operation and the DecisionPoint collects all possible refinement operations for the given flaw.
	\item Line 10: We keep trying until the chosen flaw is resolved, or until we run out of resolvers to try.
	\item Line 11: A new partial plan is obtained by application of a refinement operator. Note that the ordering over refinement operators to select is a non-deterministic step.
	\item Line 13: Recursive call to solve the new planning problem. If successful, then we are done.
	\item Line 14: Otherwise, retract the last refinement operation and move on to try the next one.
	\item Line 17:  If we arrive here, then we have exhausted all options to resolve the flaw, including the case where no options were available initially. Thus the problem cannot be solved.
\end{enumerate}

>>>>

The Plan Space Planning algorithm described above can be implemented in many different ways depending on the approach chosen for flaw and resolver selection and for backtracking. EUROPA's built-in solver implements a chronological backtracking algorithm that is summarized in Algorithm \ref{alg:europa:solve}.
 % summarized in the figure below.

\begin{algorithm}[H]
\KwIn{PartialPlan $plan$}
\KwOut{\texttt{true} if a plan solution was found, \texttt{false} otherwise}
\Begin{
  \lIf{isInconsistent(plan)}{\Return \texttt{false}\;}\label{li:propagate}
  \BlankLine
  Flaw $flaw \leftarrow chooseFlaw(plan)$ \; \label{li:selectflaw}
  \lIf{ $\emptyset = flaw$ }{\Return \texttt{true} \;} \label{li:noflaw}
  \BlankLine
  DecisionPoint $decision \leftarrow makeDecisionPoint(flaw, plan)$ \; \label{li:decisionpt}
  \While{ $decision.hasNext()$ }{ \label{li:decisionloop}
    PartialPlan $pp \leftarrow decision.executeNext()$ \; \label{li:decide}
    \lIf{ $solve(pp)$ }{ \Return \texttt{true} \; } \label{li:recurse}
    \lElse{ $decision.undo()$ \; } \label{li:backtrack}
   }
   \Return \texttt{false} \; \label{li:noplan}
 }
\caption{$\mathrm{bool} ~ solve(plan)$}
\label{alg:europa:solve}
\end{algorithm}

@@

\begin{enumerate}
	\item Line \ref{li:propagate}: Propagate the constraints to test for inconsistency. If found to be inconsistent, then we can return false since this is a dead-end i.e. no refinements to p can yield a consistent plan.
	\item Line \ref{li:selectflaw}: Choose a flaw from the set of available flaws.
	\item Line \ref{li:noflaw}: If there are no flaws, then p is complete and we can terminate with success.
	\item Line \ref{li:decisionpt}: Otherwise we formulate a decision point which is a branch in the search space. Each choice is a particular refinement operation and the DecisionPoint collects all possible refinement operations for the given flaw.
	\item Line \ref{li:decisionloop}: We keep trying until the chosen flaw is resolved, or until we run out of resolvers to try.
	\item Line \ref{li:decide}: A new partial plan is obtained by application of a refinement operator. Note that the ordering over refinement operators to select is a non-deterministic step.
	\item Line \ref{li:recurse}: Recursive call to solve the new planning problem. If successful, then we are done.
	\item Line \ref{li:backtrack}: Otherwise, retract the last refinement operation and move on to try the next one.
	\item Line \ref{li:noplan}:  If we arrive here, then we have exhausted all options to resolve the flaw, including the case where no options were available initially. Thus the problem cannot be solved.
\end{enumerate}
